### 2016-02-11 chapters/concept.tex
slight restructuring

Schrittweise die Idee entwickeln und L\"osungswege f\"ur die gegebenen Probleme finden. Insbesondere auch verschiedene Ans\"atze vergleichen und getroffene Entscheidungen begr\"unden.

>>>>

General workflow Diagram

unstructured product line $\rightarrow$ generated feature model $\rightarrow$ optimizing (via SAT-solver?) $\rightarrow$ domain knowledge of an expert $\Rightarrow$ Questionnaire $\rightarrow$ Feature model + Questionnaire $\Rightarrow$ Product (variant)

\subsection{Extraction of a feature model}
Describe the conventions and which rules are applied to generate a feature model out of it.

\subsection{Questionnaire Approach}
Use benefits of the existing approaches and overcome their shortcomings to solve the problem. State different variants and show the best one through comparison.

### 2016-02-11 chapters/intro.tex
slight restructuring

@@

Simplifying the process of configuration of productlines in FeatureIDE

This\cite{fpe} is\cite{qdc} a\cite{qbvm} dummy to create citations.

>>>>

\section*{Problem statement}
Very high complexity of configuration due to many features and constraints. Domain knowledge is highly required to understand the given software product-line and being able to combine it's features to a valid configuration which satisfies the users needs.

@@

Simplifying the process of configuration of product lines through extracting a feature model out of naming conventions and configuration files from an existing product line in FeatureIDE and applying a configuration wizard which guides the user though the creation of a specific product (variant) in the style of a questionnaire, thus applying the domain knowledge of an expert.

This\cite{fpe} is\cite{qdc} a\cite{qbvm} dummy\cite{fmgp} to create citations.
